---
title: "Analysis Exploratory Data (AED) on krill length structure from KRILLBASE"
subtitle: "Alternative Analysis to incorporate in Krill Stock Assessment Model 48.1 SubArea"
author: "Mardones, M"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

## Background

The following code perform as an Analisys Exploratory Data of Krill *Euphausia superba* based in Area 481, and with special emphasis on the proposed new management strata. The idea is to observe and prepare the days to incorporate into the stock assessment. This data base was download from [KRILLDATA Base](https://apex.nerc-bas.ac.uk/f?p=198:1:0).

## Set up and libraries

```{r setup1}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      dev = 'jpeg',
                      dpi = 300)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```


```{r}
library(tidyverse)
library(ggridges)
library(readr)
library(sp)
library(sf)
library(CCAMLRGIS)
library(ggthemes)
```

## Load data and a glimpse about structure

```{r}
Net_haul_details <- read.csv("Net haul details.csv",sep=",")
names(Net_haul_details)
dim(Net_haul_details)
table(Net_haul_details$Source)
```

Fist thing is select main columns, like 

```{r}
Net_fill <- Net_haul_details %>% 
  select(c(-2,-15, -29))
```

Ungrouping data to get raw count in all dataframe

```{r warning=FALSE}
net_glo <- Net_fill %>% 
  type.convert(as.is = TRUE) %>% 
  uncount(Total.krill.in.sample)
```


## Plot sizes composition in global data (all Southern Ocean)

```{r warning=FALSE, fig.width=3, fig.height=5}
jzglo <- ggplot(net_glo ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year)))+
  geom_density_ridges(stat = "density_ridges", bins = 30, 
                      scale = 3.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2017, by = 3))+
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzglo
```
## Group and join krill base data in Stratas
We define spatial scale, in this case, Strata from 48.1

```{r}
# Cargo linea de costa
coast <- load_Coastline()
coast1<- st_as_sf(coast) 
coast2 = st_transform(coast1, "+proj=latlong +ellps=WGS84")
# Uso las agrupaciones de Strata
strata <- st_read("~/DOCAS/Mapas/Antarctic_SHPfiles/Strata.shp",
                quiet=T)
strata=st_transform(strata, "+proj=latlong +ellps=WGS84")
```


transform data to `sf` object.

```{r}
Net_fill2 <- st_as_sf(Net_fill %>% 
                     drop_na(Latitude..dec.degrees.), 
                   coords = c("Longitude..dec.degrees.", "Latitude..dec.degrees."),  
                  crs = "+proj=latlong +ellps=WGS84")
```

Show strata agregation to join length data.

```{r maptest, fig.cap="Strata Maps in 48.1"}
# y testeo el mapa
ssmap <- ggplot()+
  geom_sf(data = strata, aes(fill=strata$ID, 
                           alpha=0.3))+
  # geom_sf(data = ssmu481aa, aes(fill=ssmu481aa$GAR_Short_Label, 
  #                         alpha=0.3))+
  geom_sf(data = coast2, colour="black", fill=NA)+
  #geom_sf(data = gridcrop1, colour="black", fill=NA)+
  #geom_sf(data= suba1aa, fill=NA)+
  # geom_sf(aes(fill=ssmu481aa$GAR_Short_Label,
  #              alpha=0.3))+
  scale_fill_viridis_d(option = "F",
                       name="Strata")+
  #geom_sf_label(aes(label = strata$ID))+
  # labs(fill = "SSMU")+
  ylim(230000, 2220000)+
  xlim(-3095349 , -1858911)+
  # coord_sf(crs = 32610)+ #sistema de prpyecccion para campos completos
  coord_sf(crs = 6932)+
  scale_alpha(guide="none")+
  theme_bw()
ssmap
```
## Join

```{r}
# comoprobar si tengo datos duplicados
strata2 <- st_make_valid(strata)
dat_len_strata <- st_join(strata2, Net_fill2)
```



Expand frecuency data related length, in this case `amount` column have frecuency that we need expand to whole data frame. 

```{r}
dat_len_strata2 <- as.data.frame(dat_len_strata)
```

## uncount frecuency in this data based on strata

```{r warning=FALSE}
df <- dat_len_strata2 %>% 
  type.convert(as.is = TRUE) %>% 
  uncount(Total.krill.in.sample)
```


## Plot total by year in 48.1

```{r warning=FALSE, fig.width=4, fig.height=5}
jzs <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year)))+
  geom_density_ridges(stat = "density_ridges", bins = 30, 
                      scale = 3.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzs
```


## Plot by year and Strata

```{r warning=FALSE}
jzstrata <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year),
                       (fill=Cruise)))+
  geom_density_ridges(stat = "density_ridges",
                      bins = 30, 
                      scale = 2.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  scale_fill_viridis_c()+
  facet_grid(.~ID) +   
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzstrata
```

## Calculate trends in mean lenght by Strata and year
```{r}
dfgru <- df %>% 
  group_by(Year, ID) %>% 
  summarize(MEANL =mean(Mean.length..mm.))
```

## Means trends in krill base by year and strata
```{r}
lmlenght <- ggplot(dfgru,
                   aes(Year, MEANL))+
                   #colour=CLASS))+
    geom_point(show.legend = F,
               shape=21) +
    geom_smooth(method= "lm",
                color="blue",
               alpha=0.6)+
    #scale_size(range = c(-4,8)) +
     theme_few()+ 
    facet_wrap(.~ID)+
    geom_hline(yintercept = 40, color = "red")+
    scale_x_continuous(breaks = seq(from = 1927, to = 2021, by = 5))+
    theme(axis.text.x = element_text(angle = 90, hjust = 2))+
    guides(fill = guide_legend(reverse=F))+
    scale_fill_viridis_d(option="G")+
    ylim(0,80)+
    ylab("Mean length (mm.)") +
    xlab("") +
    ggtitle("Lenght Mean. KRILLBASE data")
lmlenght
```

## krill data lenght by Source and year. (i need  improve this visualization||)

```{r eval=FALSE, warning=FALSE, message=FALSE}
jzsnet <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year)))+
  geom_density_ridges(stat = "density_ridges",
                      bins = 30, 
                      scale = 1.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  scale_fill_viridis_c()+
  facet_grid(~Source) +   
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzsnet
```



```{r eval=FALSE}
# cut in order
df$catlon <- cut(x = df$length, 
                 breaks = seq(0,70,2),
                 labels = seq(0,68,2),
                 right = FALSE)

dft <- table(df$Year, df$catlon)
```


```{r eval=FALSE}
write.csv(dft, "lenghtkrillbase19262007.csv", sep = ",", row.names = TRUE)

```

