---
title: "Data prepair Length structure KRILLBASE"
subtitle: "Alternative Analysis to incorporate in Krill Stock Assessment Model 48.1 SubArea"
author: "Mardones, M"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup1}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      dev = 'jpeg',
                      dpi = 300)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```


```{r}
library(tidyverse)
library(ggridges)
library(readr)
library(sp)
library(sf)
library(CCAMLRGIS)
library(ggthemes)
```

# Background

The following document intends to carry out a complementary
methodological analysis to correlate environmental variables with the
population dynamics of krill (*Euphausia superba*), in this case, with a
biological component like lengths from fishery monitoring.


# Methodology

Load data 

```{r}
Net_haul_details <- read.csv("Net haul details.csv",sep=",")
names(Net_haul_details)
dim(Net_haul_details)
table(Net_haul_details$Year)
```

Fist thing is select main columns, like 

```{r}
Net_fill <- Net_haul_details %>% 
  select(c(-2,-15, -28, -29))
```


We define spatial scale, in this case, Strata from 48.1

```{r}
# Cargo linea de costa
coast <- load_Coastline()
coast1<- st_as_sf(coast) 
coast2 = st_transform(coast1, "+proj=latlong +ellps=WGS84")
# Uso las agrupaciones de Strata
strata <- st_read("~/DOCAS/Mapas/Antarctic_SHPfiles/Strata.shp",
                quiet=T)
strata=st_transform(strata, "+proj=latlong +ellps=WGS84")
```


transfrom data to `sf` object.

```{r}
Net_fill2 <- st_as_sf(Net_fill %>% 
                     drop_na(Latitude..dec.degrees.), 
                   coords = c("Longitude..dec.degrees.", "Latitude..dec.degrees."),  
                  crs = "+proj=latlong +ellps=WGS84")
```

Show strata agregation to join length data (Figure\@ref(fig:maptest).

```{r maptest, fig.cap="Strata Maps in 48.1"}
# y testeo el mapa
ssmap <- ggplot()+
  geom_sf(data = strata, aes(fill=strata$ID, 
                           alpha=0.3))+
  # geom_sf(data = ssmu481aa, aes(fill=ssmu481aa$GAR_Short_Label, 
  #                         alpha=0.3))+
  geom_sf(data = coast2, colour="black", fill=NA)+
  #geom_sf(data = gridcrop1, colour="black", fill=NA)+
  #geom_sf(data= suba1aa, fill=NA)+
  # geom_sf(aes(fill=ssmu481aa$GAR_Short_Label,
  #              alpha=0.3))+
  scale_fill_viridis_d(option = "F",
                       name="Strata")+
  #geom_sf_label(aes(label = strata$ID))+
  # labs(fill = "SSMU")+
  ylim(230000, 2220000)+
  xlim(-3095349 , -1858911)+
  # coord_sf(crs = 32610)+ #sistema de prpyecccion para campos completos
  coord_sf(crs = 6932)+
  scale_alpha(guide="none")+
  theme_bw()
ssmap
```


```{r}
# comoprobar si tengo datos duplicados
strata2 <- st_make_valid(strata)
dat_len_strata <- st_join(strata2, Net_fill2)
```



Expand frecuency data related length, in this case `amount` column have frecuency that we need expand to whole data frame. 

```{r}
dat_len_strata2 <- as.data.frame(dat_len_strata)
```


```{r warning=FALSE}
df <- dat_len_strata2 %>% 
  type.convert(as.is = TRUE) %>% 
  uncount(Total.krill.in.sample)
```
by year

```{r warning=FALSE, fig.width=3, fig.height=6}
jzs <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year)))+
  geom_density_ridges(stat = "density_ridges", bins = 30, 
                      scale = 3.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzs
```


by strata

```{r warning=FALSE}
jzstrata <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year),
                       (fill=Cruise)))+
  geom_density_ridges(stat = "density_ridges",
                      bins = 30, 
                      scale = 2 %>% .9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  scale_fill_viridis_c()+
  facet_grid(.~ID) +   
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzstrata
```

by net type

```{r eval=FALSE, warning=FALSE, message=FALSE}
jzsnet <- ggplot(df ,
                   aes(x=Mean.length..mm., 
                       y = as.factor(Year),
                       (fill=Cruise)))+
  geom_density_ridges(stat = "density_ridges",
                      bins = 30, 
                      scale = 1.9, 
                      draw_baseline = FALSE,
                      alpha=0.9)+
  scale_fill_viridis_c()+
  facet_grid(~Nettype) +   
  geom_vline(xintercept = 40, color = "red")+
  scale_x_continuous(breaks = seq(from = 10, to = 80, 
                                  by = 10))+
  scale_y_discrete(breaks = seq(from = 1926, 
                                to = 2007, by = 3))+
  scale_fill_viridis_d(name="Strata",
                       option="H")+
  
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2))+
  xlab("Length (mm.)")+
  ylab("")
jzsnet
```



```{r eval=FALSE}
# cut in order
df$catlon <- cut(x = df$length, 
                 breaks = seq(0,70,2),
                 labels = seq(0,68,2),
                 right = FALSE)

dft <- table(df$Year, df$catlon)
```


```{r eval=FALSE}
write.csv(dft, "lenghtkrillbase19262007.csv", sep = ",", row.names = TRUE)

```

